Extinction simulation on the metaweb

### 2022-10-24 random_network.Rmd
Switched all figures and analysis to targets

```{r}
get_fw_metrics <- function(x) {

  ff_metaweb <- get_fish_fish_matrix(x)

  if (ncol(ff_metaweb) == 0) {
    ff_ind <- NA
    ct_ff <- NA
    tl_ff <- NA
    avg_tl_ff <- NA
    max_tl_ff <- NA
  } else {
    ff_ind <- NetIndices::GenInd(ff_metaweb)
    ct_ff <- ff_ind["C"]
    tl_ff <- NetIndices::TrophInd(ff_metaweb)$TL
    avg_tl_ff <- mean(tl_ff)
    max_tl_ff <- max(tl_ff)
  }

  ind <- NetIndices::GenInd(x)
  ct <- ind["C"]
  tl <- NetIndices::TrophInd(x)$TL
  avg_tl <- mean(tl)
  max_tl <- max(tl)

  list(
    ff_metaweb = ff_metaweb,
    ind = ind,
    ff_ind = ff_ind,
    ct = ct,
    ct_ff = ct_ff,
    tl = tl,
    tl_ff = tl_ff,
    avg_tl = avg_tl,
    avg_tl_ff = avg_tl_ff,
    max_tl = max_tl,
    max_tl_ff = max_tl_ff
  )
}

get_fw_metrics2 <- function(x, keep_metaweb = TRUE) {

  ff_metaweb <- get_fish_fish_matrix(x)

  if (ncol(ff_metaweb) == 0) {
    ff_ind <- NA
    ct_ff <- NA
    tl_ff <- NA
    avg_tl_ff <- NA
    max_tl_ff <- NA
  } else {
    ff_ind <- NA
    ct_ff <- sum(ff_metaweb) / (ncol(ff_metaweb) - 1)^2
    tl_ff <- NetIndices::TrophInd(ff_metaweb)$TL
    avg_tl_ff <- mean(tl_ff)
    max_tl_ff <- max(tl_ff)
  }

  if (ncol(x) == 0) {
    ind <- NA
    ct <- NA
    tl <- NA
    avg_tl <- NA
    max_tl <- NA
  } else {
    ind <- NA
    ct <- sum(x) / (ncol(x) - 1)^2
    tl <- NetIndices::TrophInd(x)$TL
    avg_tl <- mean(tl)
    max_tl <- max(tl)
  }

  if (!keep_metaweb) {
    ff_metaweb <- NA
  }

  list(
    ff_metaweb = ff_metaweb,
    ind = ind,
    ff_ind = ff_ind,
    ct = ct,
    ct_ff = ct_ff,
    tl = tl,
    tl_ff = tl_ff,
    avg_tl = avg_tl,
    avg_tl_ff = avg_tl_ff,
    max_tl = max_tl,
    max_tl_ff = max_tl_ff
  )

}

get_sim_net <- function(net = NULL, ext_seq = NULL, keep_metaweb = TRUE) {

  node_extinction <- tibble(
    node_rm_single = names(ext_seq),
    node_tlvl = ext_seq,
    node_rm_tot = map(seq_along(ext_seq),
      ~ext_seq[1:.x]),
    metaweb = furrr::future_map(
      seq_along(ext_seq),
      ~metaweb[
        !rownames(net) %in% names(ext_seq)[1:.x],
        !colnames(net) %in% names(ext_seq)[1:.x]
        ]
    )
  )

  meta_keep <- keep_metaweb
  out <- node_extinction %>%
    mutate(
      metrics = furrr::future_map(
        metaweb, ~try(get_fw_metrics2(.x, keep_metaweb = meta_keep))
      )
    )

  if (!keep_metaweb) {
    out$metaweb <- NULL
  }

  return(out)
}

```

@@

```{r random-richness, eval = FALSE}
sim_dec_tlvl_species <- vector(mode ="list", length = length(fish_species_tlvl)) 
sim_inc_tlvl_species <- vector(mode = "list", length = length(fish_species_tlvl))
inc_species_tlvl <- sort(fish_species_tlvl, decreasing = FALSE)

for (i in seq_along(fish_species_tlvl)) {
  decreasing_tlvl_metaweb <- metaweb[
    !str_detect(
      rownames(metaweb),
      paste0(names(fish_species_tlvl)[1:i], collapse = "|")
      ),
    !str_detect(
      colnames(metaweb),
      paste0(names(fish_species_tlvl)[1:i], collapse = "|")
      )
    ]
  sim_dec_tlvl_species[[i]] <- get_fw_metrics2(decreasing_tlvl_metaweb,
    keep_metaweb = FALSE)

  increasing_tlvl_metaweb <- metaweb[
    !str_detect(
      rownames(metaweb),
      paste0(names(inc_species_tlvl)[1:i], collapse = "|")
      ),
    !str_detect(
      colnames(metaweb),
      paste0(names(inc_species_tlvl)[1:i], collapse = "|")
      )
    ]
  sim_inc_tlvl_species[[i]] <- get_fw_metrics2(increasing_tlvl_metaweb,
    keep_metaweb = FALSE)
}
dec_species_result <- tibble(
  one_sp_rm = names(fish_species_tlvl),
  species_removed = map(seq_along(fish_species_tlvl),
    ~names(fish_species_tlvl)[1:.x]),
  metrics = sim_dec_tlvl_species
  )

inc_species_result <- tibble(
  one_sp_rm = names(inc_species_tlvl),
  species_removed = map(seq_along(inc_species_tlvl),
    ~names(inc_species_tlvl)[1:.x]),
  metrics = sim_inc_tlvl_species
  )
save(file = mypath("data", "sim_dec_sp_tlvl.rda"), dec_species_result)
save(file = mypath("data", "sim_inc_sp_tlvl.rda"), inc_species_result)
```

```{r, eval = FALSE}
# random simulation
nsim <- 10
set.seed(123)

sim_random_tlvl_species <- vector(mode = "list", length = length(fish_species_tlvl))
sim_random_tlvl_species <- map(sim_random_tlvl_species, ~vector(mode = "list", length = nsim))
sp_to_rm <- vector(mode = "list", length = length(fish_species_tlvl))
sp_to_rm <- map(sp_to_rm, ~vector(mode = "list", length = nsim))

for (i in seq_along(fish_species_tlvl)) {

  for (j in seq_len(nsim)) {
    sp_to_rm[[i]][[j]] <- sample(names(fish_species_tlvl), size = i, replace = FALSE)

    tmp_metaweb <- metaweb[
      !str_detect(
        rownames(metaweb),
        paste0(sp_to_rm[[i]][[j]], collapse = "|")
        ),
      !str_detect(
        colnames(metaweb),
        paste0(sp_to_rm[[i]][[j]], collapse = "|")
      )
      ]
    sim_random_tlvl_species[[i]][[j]] <- get_fw_metrics2(
      tmp_metaweb,
    keep_metaweb = FALSE)
  }
}

random_species_result <- tibble(
  nsp_rm = seq_along(fish_species_tlvl),
  species_removed = sp_to_rm,
  metrics = sim_random_tlvl_species
  )
save(file = mypath("data", "sim_random_sp_tlvl.rda"), random_species_result)
```

>>>>

```{r}
```

@@

```{r random-richness, eval = FALSE}
save(file = mypath("data", "sim_dec_sp_tlvl.rda"), dec_species_result)
save(file = mypath("data", "sim_inc_sp_tlvl.rda"), inc_species_result)
```

```{r, eval = FALSE}
# random simulation
save(file = mypath("data", "sim_random_sp_tlvl.rda"), random_species_result)
```
